Increased productivity using Atomify - a real-time LAMMPS visualizer

### 2018-06-13 IOPLaTeX.tex
Yeah, more stuff

\subsection{Measurement setup}
We will use the built-in binning feature in LAMMPS called \textit{chunks}, a very general concept where you assign a \code{chunkID} to each atom
based on its position. LAMMPS supports multiple different \textit{chunk styles}, one of which is cylinder.
In the cylinder binning, we choose the same properties as for a cylinder region (center, length etc), but also the binsize in the length direction and how many radial bins we want.
We only want one bin in the flow direction since we will measure the radial velocity profile only.
The command for giving each atom a \code{chunkID} is\footnote{The \& is used to continue the command on the next line.}
\begin{lstlisting}
compute chunk all chunk/atom bin/cylinder x lower &
$(lx) $c $c 0 $R 30 units box
\end{lstlisting}
See the documentation for details about this command, but note that the binsize in the length direction is equal to the system length so we only get one bin.
It will create 30 radial bins for $r\in (0, R)$, where $R$ is the radius of the inner cylinder.
The final command we will use is the \code{fix ave/chunk} where we can get a smooth averaged velocity profile sampled over many timesteps.
To obtain this, we simply use
\begin{lstlisting}
fix vx all ave/chunk 10 10 100 chunk vx ave running
\end{lstlisting}
Here we use every 10th value to sample the velocity profile, keeping all samples to sum them into a large histogram.
This fix will appear in the list of fixes in the Simulation summary just as groups, regions, computes and variables.
When we click it, we will get the figure shown in figure \ref{fig:velocity_profile1}.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{lj_flow/08_velocity_profile1.png}
	\caption{
		The velocity profile for a Lennard Jones gas inside a nanochannel of radius 8.7 (reduced units).
		Since the wall also is made of Lennard Jones atoms, some of the wall atoms
		This figure is made using the Atomify real-time plotter which can show any scalar value defined in LAMMPS
		as compute, fix or variable.
    }
	\label{fig:velocity_profile1}
\end{figure}

\subsection{Results}

\begin{figure}
	\centering
	% \includegraphics[width=0.5\textwidth]{lj_flow/07_moving.png}
	\caption{
		Velocity profiles for different densities.
		The step flow shape is evident for low density gases with a high non-zero slip velocity.
		When the density increases, the slip velocity goes to zero as expected.
    }
	\label{fig:velocity_profiles}
\end{figure}

We conclude this case study with a series of simulations of the system described above for different densities $\rho$.
Each simulation runs 10000 timesteps before we export the plots from \code{fix vx} to MATLAB using the Export function seen in figure \ref{fig:velocity_profile1}.
All these plots are now merged into a final figure which is shown in figure \ref{fig:velocity_profiles}.
It is here evident that the velocity near the boundary is not zero, which is the reason why the permeability is much higher for dilute gases than dense liquids.
This is, as mentioned earlier, called the Klinkenberg effect\cite{klinkenberg1941permeability}.

\section{\label{sec:discussion}Discussion}
In this paper we have presented Atomify, an application that reduces the large amount of context switches and mouse clicks
when creating new simulation scripts.
As of today, only LAMMPS is supported as the physical simulator, but other codes can easily be integrated
due our general implementation with no assumpetion about the underlying code except atom positions.
The communication overhead is minimized since LAMMPS runs in the same process as Atomify, sharing the memory.

\section{\label{sec:future}Future work}
Atomify continues in heavy development and we have several features planned for future versions.
We already have a simple version of Atomify in the web browser using WebGL and WebAssembly.
This makes it easy to test scripts in the browser with all simple functionalities available.
This is especially useful in educational settings where teachers wish to introduce students
to LAMMPS without installing additional software.
It will also serve as a nice demonstration of the full desktop application of Atomify.

@@

\section{Acknowledgments}

\section{Disclosure}

Svenn-Arne Dragly is employed part-time by The Qt Company.

\bibliography{Remote}

%\section*{References}
%\begin{thebibliography}{10}
%\bibitem{ref1} J.~Doe, Article name, \textit{Phys. Rev. Lett.}

>>>>

\subsection{Measurement setup}
We will use the built-in binning feature in LAMMPS called \textit{chunks}, a very general concept where you assign a \code{chunkID} to each atom
based on its position. LAMMPS supports multiple different \textit{chunk styles}, one of which is cylinder.
In the cylinder binning, we choose the same properties as for a cylinder region (center, length etc.), but also the binsize in the length direction and how many radial bins we want.
We only want one bin in the flow direction since we only want to measure the radial velocity profile.
The command for giving each atom a \code{chunkID} is\footnote{The \& is used to continue the command on the next line since it is quite long.}
\begin{lstlisting}
compute chunk all chunk/atom bin/cylinder x lower &
$(lx) $c $c 0 $R 30 units box
\end{lstlisting}
It will create 30 radial bins for $r\in (0, R)$, where $R$ is the radius of the inner cylinder.
The final command we will use is the \code{fix ave/chunk} where we can get a smooth averaged velocity profile sampled over many timesteps.
To obtain this, we use
\begin{lstlisting}
fix vx all ave/chunk 10 10 100 chunk vx ave running
\end{lstlisting}
Here we use every 10th value to sample the velocity profile, keeping all samples to sum them into a larger histogram.
This fix will appear in the list of fixes in the \textit{Simulation summary} just as groups, regions, computes and variables.
When we click it, we will get the figure shown in figure \ref{fig:velocity_profile1}.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{lj_flow/08_velocity_profile1.png}
	\caption{
		The velocity profile for a Lennard Jones gas inside a nanochannel of radius 8.7 (reduced units).
		Since the wall also is made of Lennard Jones atoms, some of the wall atoms
		This figure is made using the Atomify real-time plotter which can show any scalar value defined in LAMMPS
		as compute, fix or variable.
    }
	\label{fig:velocity_profile1}
\end{figure}
\todo{Create fig 6 with both one single velocity profile and MATLAB plot of all of them. Maybe W/H = 0.5?}
\subsection{Results}
We conclude this case study with a series of simulations of the system described above for different densities $\rho$.
Each simulation runs 10000 timesteps before we export the plots from \code{fix vx} to MATLAB using the Export function seen in figure \ref{fig:velocity_profile1}.
All these plots are now merged into a final figure which is shown in figure \ref{fig:velocity_profiles}.
It is here evident that the velocity near the boundary is not zero, which is the reason why the permeability is much higher for dilute gases than dense liquids.
This is, as mentioned earlier, called the Klinkenberg effect\cite{klinkenberg1941permeability}.

\section{\label{sec:discussion}Discussion}
In this paper we have presented Atomify, an new software that reduces the amount of context switches and mouse clicks
when developing new simulation scripts.
As of today, only LAMMPS is supported as the physical simulator, but other codes can easily be integrated
due our general implementation with no assumpetion about the underlying code except atom positions.
The communication overhead is minimized since LAMMPS runs in the same process as Atomify, sharing the memory.

@@

\section{Acknowledgments}
Statoil etc.

\section*{References}
\bibliography{Remote}

%
%\begin{thebibliography}{10}
%\bibitem{ref1} J.~Doe, Article name, \textit{Phys. Rev. Lett.}
